Reanalysis Step 3: Propensity Score Analysis with Twang

### 2025-08-19 reanalysis-3-propensity_scores.qmd
fix plot output

```{r diagnostics-loop}
# Generate diagnostic plots for selected imputations
for (i in imps_to_show) {
  cat("\n### Imputation", i, "\n\n")

  twang_model <- twang_results[[i]]$model

  cat("#### Convergence\n")
  plot(twang_model, plots = 1)

  cat("\n#### Weight Distribution\n")
  plot(twang_model, plots = 2)

  cat("\n#### Covariate Balance\n")
  plot(twang_model, plots = 3)

  cat("\n#### Weight Proportions\n")
  plot(twang_model, plots = 6)

  cat("\n#### Balance Summary Table\n")
  print(summary(twang_model))
}
```

>>>>

```{r diagnostics-loop}
#| results: "asis"

# Generate diagnostic plots for selected imputations
for (i in imps_to_show) {
  cat("\n### Imputation", i, "\n\n")

  twang_model <- twang_results[[i]]$model
  weights <- twang_results[[i]]$weights

  # Create dataset with weights for cobalt
  data_with_weights <- imputed_datasets[[i]]
  data_with_weights$weights <- weights

  cat("#### Convergence (Iteration Plot)\n\n")
  # Plot 1: Shows how balance metrics change across iterations
  plot(twang_model, plots = 1)
  cat("\n\n")

  cat("#### Weight Distribution (Boxplot)\n\n")
  # Plot 2: Shows distribution of weights
  plot(twang_model, plots = 2)
  cat("\n\n")

  cat("#### Covariate Balance (Standardized Mean Differences)\n\n")
  # Plot 3: Shows balance for each covariate
  plot(twang_model, plots = 3)
  cat("\n\n")

  cat("#### Alternative Balance Plot (Love Plot)\n\n")
  # Use cobalt for better visualization
  library(cobalt)
  love_plot <- love.plot(
    bal.tab(ps_formula, 
            data = data_with_weights,
            weights = "weights",
            estimand = "ATT",
            s.d.denom = "treated"),
    thresholds = c(m = 0.1),
    title = paste("Covariate Balance - Imputation", i)
  )
  print(love_plot)
  cat("\n\n")

  cat("#### Weight Proportions\n\n")
  # Plot 6: Histogram of weight proportions
  plot(twang_model, plots = 6)
  cat("\n\n")

  cat("#### Balance Summary Table\n\n")
  print(summary(twang_model))
  cat("\n\n")
}
```
